Meta Analysis for Optimal Run-time Checking

### 2018-01-26 paper.tex
brainstorming in 1-1 with Jared

%% For double-blind review submission
\documentclass[acmlarge,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission
%\documentclass[acmlarge,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[acmlarge]{acmart}\settopmatter{}

@@

@@

Req: program, programmer-provided annotation (to be discharged), analysis to be used to discharge the annotation, semantics for stepping program
Tool:
    Run analysis at each step, identify stoplight for annotation (red/yellow/green)
        Modify analysis to handle running in-program? (several options)
    Identify steps where stoplight result \textit{changes}
    Return to user: location of optimal check, or perhaps "can't verify"

@@

>>>>

%% For double-blind review submission
\documentclass[acmlarge,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission
%\documentclass[acmlarge,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission
%\documentclass[acmlarge]{acmart}\settopmatter{}

@@

\usepackage{listings}

@@

Req: program, programmer-provided annotation (to be discharged), analysis to be used to discharge the annotation, semantics for stepping program

Tool:

Run analysis at each step, identify stoplight for annotation (red/yellow/green)

Modify analysis to handle running in-program? (several options)

Identify steps where stoplight result \textit{changes}

Return to user: location of optimal check, or perhaps "can't verify"

@@

\begin{lstlisting}
1 a := new int[10];
2 r := rand();
3 if r < magicval then
4   x := 5
5 else
6   x := 15
7 return a[x]    
\end{lstlisting}
\begin{tabular}{l|l|l}
  \multicolumn{3}{c}{\textbf{Analysis results for x at entry to line 7 }}
  \\
  Concrete execution & (Offline) Meta Analysis & Online Analysis
  \\
  \hline 
  1 exit & undet          & [5, 15]
  \\
  2 exit & det / redgreen & [5,5] \emph{WORLD-OR} [15,15]
  \\
  3 exit & det            &
  \\
  4 exit & $\vdots$       
  \\
  5 exit
  \\
  6 exit
  \\
  7 exit
\end{tabular}

Standard interval analysis result for x at entry to 7 is [5, 15].
